### 2019-11-28 Mathematical Statistics/ms_ch_04.rmd
ms ch4 & cf ch2
ms ch4 & cf ch2

>>>>

### 4.5

Consider two populations A = {3, 5, 7, 9, 10, 16}, B = {8, 10, 11, 15, 18, 25, 28}.

```{r, echo = T}
A <- c(3, 5, 7, 9, 10, 16)
B <- c(8, 10, 11, 15, 18, 25, 28)
```

a.) Using R, draw random samples (without replacement) of size 3 from each population, and simulate the sampling distribution of the sum of their maximums.

```{r, echo = T, fig.height=3.5, fig.width=8}
```

Describe the distribution.

b.) Use your simulation to estimate the probability that the sum of the maximums is less than 20.

```{r, echo = T}
```

c.) Draw random samples of size 3 from each population, and find the maximum of the union of these two sets.

Simulate the sampling distribution of the maximums of this union.

Compare the distribution to part (a).

d.) Use simulation to find the probability that the maximum of the union is less than 20.

### 4.6
